### 2019-05-01 README.Rmd
fix bug in breadwheat
checks

The package is under development, so be patient and have fun! We appreciate that issues to be reported in our issues section on Github.

>>>>

## Installation

The development version can be installed via

    library("devtools")
    devtools::install_github("kauedesousa/gosset", upgrade = "never")

**gosset** is under development. Use with caution.

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
